Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-30 inst/paper/main.tex
minor

\subsubsection{Does eval introduce new bindings}
Find number of times, eval introduces new bindings. There are many
ways -- library, load, attach, source, and explicitly introduce
bindings using super-assign, assign and define.

\subsubsection{Does eval call C code}
Find number of times, eval makes call to native code using - .Call,
.External, etc. Find out if there are native functions that are called
only from within eval.

\subsubsection{Does eval add finalizers}
Eval can attach code to be executed when the object goes out of scope
or program exits. Find if eval does that.

\subsubsection{Does eval do non-local returns}
Eval can do non-local returns effective bypassing evaluation of the
rest of the function. This can be useful for static analyzers.

Conclude with number of evals that are ``pure'', i.e. evals which
could be ignored by a static analyzer without any problem.

@@

\subsubsection{Side-Effects}

>>>>

\mypara{New Bindings.} Find number of times, eval introduces new
bindings. There are many ways -- library, load, attach, source, and
explicitly introduce bindings using super-assign, assign and define.

\mypara{C Calls.} Find number of times, eval makes call to native code
using - .Call, .External, etc. Find out if there are native functions
that are called only from within eval.

\mypara{Non-local returns}
Eval can do non-local returns effective bypassing evaluation of the
rest of the function. This can be useful for static analyzers.

\mypara{Purity.}
Conclude with number of evals that are ``pure'', i.e. evals which
could be ignored by a static analyzer without any problem.

@@
